Barneby Lives!

### 2023-05-10 scripts/taxonomy_setup.Rmd
spell check function

@@

dropped_infra <- search_powo("Ivesia lycopodioides var. lycopodioides")
valid_binomial <- search_powo("Ivesia lycopodioides")
kept_infra <- search_powo("Potentilla lycopodioides var. megalopetala")
what_do_w_authority_autonyms <- search_powo("Potentilla lycopodioides var. lycopodioides")

powo_searcher("Potentilla lycopodioides var. megalopetala")
powo_searcher("Potentilla lycopodioides var. lycopodioides")

lapply(c('Poa annua', 'Linnaea borealis'), powo_searcher)

test <- WorldFlora::WFO.match(
  spec.data = WFO.example, 
   spec.name = 'binomial',
   Fuzzy = 0.1)

family_spellings <- vascular.families %>% 
  dplyr::pull(Family)

pec.test <- data.frame(spec.name=c("Faidherbia albida", "Acacia albida",
"Faidherbia albidum", "Faidherbia albidus",
"Faidherbia albiida",
"Prunus africanus", "Prunos africanea",
"Prunus afrocaneus", "Prunus afrocaneos"))

match1 <- WFO.match.fuzzyjoin(spec.data=spec.test, WFO.data=WFO.example,
fuzzydist.max = 6)
```

>>>>

# the first letter of the genus must be correct, 
# the first three letters of the species must be correct

cla <- data.table::fread('../taxonomic_data/WFO_Backbone/classification.txt')
genLKPtab <- unique(cla, by = 'genus')[taxonomicStatus == 'Accepted','genus'] %>% 
  arrange(genus) %>% 
  mutate(Grp = str_extract(genus, '[A-Z][a-z]{1}'))%>% 
  rename(strings = genus)

speLKPtab <- unique(cla, by = 'specificEpithet')[
  taxonomicStatus == 'Accepted','specificEpithet'] %>% 
  arrange(specificEpithet) %>% 
  mutate(Grp = str_extract(specificEpithet, '[a-z]{3}')) %>% 
  rename(strings = specificEpithet)

spell_check('Poa annua') # works
spell_check('Poar annua') # works
spell_check('Poa annur') # works
spell_check('Poar annur') # works
spell_check('Pou annua') # works

@@

```{r}
lapply(c('Cryptantha glomerata', 'Sphenosciadium capitellatum'), powo_searcher)
```
